\chapter{Project Description}
The following text is the project description pulled from the project catalog. \newline

Development of multi-channel audio/video playback system for touring artists. This project will
integrate both hardware- and software-design with emphasis on hardware design.
Approx. 70-80 percent of modern Danish and international touring artists utilize audio backing tracks
(prerecorded material played back on some chosen device) and video content projected on large
screens as part of their performance. \\
However, there are a multitude of options ranging from iPod-playback to complex, customized
systems operated by technical personnel. \\
Common for these systems is instability, making artists to purchase redundant backup-systems in
order to deliver their audience a flawless and uninterrupted performance. \newline

In a typical scenario, at least one laptop – often several laptops – with various audio- and/or videointerfaces, handles and runs the audio backing track and video-content in sync. \newline

This project will integrate both audio- and video-handling in a single 19” rack-mounted device and
provide the user with a user-friendly GUI (Graphical User Interface) while complying with
international standards for audio and video and electronic devices. \newline

For design and implementation of the device, a research is needed in: \\
- Circuit/hardware design \\
- D/A audio converters \\
- Standardized audio input/output formats \\
- Audio file formats \\
- Standardized video input/output formats \\
- Video file formats \\
- Time codes for synchronization \\
- User feedback for feasible GUI design \newline

This project is already in the early stages of development as part of an apprenticeship in
entrepreneurship (iværksætterpraktik) at Navitas Science and Innovation. \\
Current status on project: \\
- Requirements specification finished \\
- FURPS finished \\
- Market research ongoing \\
The project is requesting confidentiality as the device is in development intended for market release to
prosumers in the music industry, thus an eventual project partner must sign a non-disclosure
agreement. \newline

Project partner profile: Electronic Engineering student or Information and Communication
Technology student.